Designing a high-performance boundary element library with OpenCL and Numba

### 2021-05-28 main.tex
Revisions done.
american spelling and add Numba reference
Added Timo Betcke biography

@@

@@

>>>>

\bibitem{erichsen}
S. Erichsen, and A. Sauter,
``Efficient automatic quadrature in 3-d Galerkin BEM,''
{\it Computer Methods in Applied Mechanics and Engineering}, vol. 157, no. 3, pp. 215--224, 1998.
\textsc{doi}: \href{https://doi.org/10.1016/S0045-7825(97)00236-3}{10.1016/S0045-7825(97)00236-3}.

@@

\bibitem{numba}
S. K. Lam, A. Pitrou, and S. Seibert,
``Numba: a LLVM-based Python JIT compiler,''
{\it Proceedings of the Second Workshop on the LLVM Compiler Infrastructure in HPC}, 2015.
\textsc{doi}: \href{https://dx.doi.org/10.1145/2833157.2833162}{10.1145/2833157.2833162}.

@@

\begin{IEEEbiography}{Timo Betcke}{\,}is Professor of Computational Mathematics in the Department of Mathematics at University College London (UCL).
He originally studied Computational Engineering at Hamburg University of Technology before pursuing a DPhil in Numerical Analysis
at the University of Oxford, from which he graduated in 2006. Before joining UCL in 2011 he has held research positions at Braunschweig,
Manchester, and Reading. His work is on the interface of numerical analysis and computational sciences. He was principal investigator
in two EPSRC software infrastructure grants for the development of Bempp and has been PI and Co-I on a number of other projects related
to boundary element methods.
\end{IEEEbiography}
